### 2019-06-08 doc/chapters/introduction.tex

Stainless statically verifies that a program satisfies a given specification and that a program will not crash at runtime.
The framework explores all possible inputs and finds a counter examples for possible failures in a program which violate the given specification.

The main functions used to write a specification are \textit{require} and \textit{ensuring}. 
With \textit{require} we define a precondition of a function, which we want to verify.
\textit{require} is placed at the beginning of the function body.
We pass a constraint for the inputs of a function as an argument to \textit{require} in the form of a Boolean expression.

With \textit{ensuring} we provide a postcondition which is a condition on an output of the function.
\textit{ensuring} is called after the function body.

On invoking, Stainless tries to prove that the postcondition always holds, assuming the given precondition does hold.

>>>>

Stainless statically verifies that a program satisfies a given specification and that a program will not crash at runtime.
The framework covers all possible inputs and finds a counter examples for possible failures in a program which violate the given specification.

The main functions used to write a specification are \textit{require} and \textit{ensuring}.

With \textit{require} we define a precondition of a function, which we want to verify.
\textit{require} is placed at the beginning of the function body.
\textit{require} specifies, if the parameter of the function hold a certain condition.

With \textit{ensuring}, we define the postcondition of a function.
\textit{ensuring} is placed at the end of the function after the body.
\textit{ensuting} specifies, if the return value or the result of the function hold a certain condition.

On invoking Stainless, it tries to prove that the postcondition always holds, assuming the given precondition does hold.
